Need Fulfillment During Intergroup Contact: Three Experience Sampling Studies

### 2023-05-30 Methods-and-Results.Rmd
descr tbl red

```{r studentVarDescr, include=FALSE}
studentMlCor <-
  MlCorMat(
    data = dtStudentSupp$studentInteractionType,
    id = "PID",
    # selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "interaction_quality", "AttitudesDutch"),
    # labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
    selection = c("KeyNeedFullfillment", "interaction_quality", "AttitudesDutch"),
    labels = c("Core Need", "Competence", "Quality", "Attitudes NL")
  )

>>>>

```{r studentVarDescr, include=FALSE}
studentMlCor <-
  MlCorMat(
    data = dtStudentSupp$studentInteractionType,
    id = "PID",
    # selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "interaction_quality", "AttitudesDutch"),
    # labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
    selection = c("KeyNeedFullfillment", "interaction_quality", "AttitudesDutch"),
    labels = c("Core Need", "Quality", "Attitudes NL")
  )

### 2023-05-30 Table.tex
descr tbl red

>>>>

\multicolumn{1}{!{\huxvb{0, 0, 0}{0}}l!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\raggedright \hspace{12pt} {\fontsize{9pt}{10.8pt}\selectfont SumContactNL} \hspace{6pt}\huxbpad{6pt}} &
\multicolumn{8}{c!{\huxvb{0, 0, 0}{0}}}{\huxtpad{6pt + 1em}\centering \hspace{6pt} {\fontsize{9pt}{10.8pt}\selectfont  0.51** [ 0.12,  0.89]; $\eta_{partial}$ = 0.03} \hspace{6pt}\huxbpad{6pt}} \tabularnewline[-0.5pt]

### 2023-05-30 Tables/studentOutVarDescr.tex
descr tbl red

\caption{\label{tab:studentOutVarDescr}Student: Multilevel Core Variable Descriptives (Outgroup Contact Only)}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llccccc}
\toprule
  & Core Need & Competence & Autonomy & Relatedness & Quality & Attitudes NL\\
\midrule
Core Need &  & 0.44** & 0.49*** & -0.22 & 0.29 & 0.15\\
Competence & 0.23*** &  & 0.58*** & 0.38** & 0.46*** & 0.22\\
Autonomy & 0.12*** & 0.25*** &  & 0.21 & 0.50*** & 0.06\\
Relatedness & 0.49*** & 0.22*** & 0.46*** &  & 0.48*** & -0.10\\
Quality & 0.19*** & 0.38*** & 0.16*** & 0.15*** &  & 0.08\\
Attitudes NL & 0.32*** & 0.36*** & 0.19*** & 0.22*** & 0.29*** & \\
\addlinespace
Grand Mean & 86.86 & 73.23 & 78.58 & 60.30 & 67.08 & 70.41\\
Between SD & 11.20 & 13.95 & 14.07 & 17.35 & 12.54 & 17.13\\
Within SD & 15.87 & 16.81 & 14.24 & 26.14 & 16.54 & 9.87\\
ICC(1) & 0.14 & 0.27 & 0.40 & 0.19 & 0.24 & 0.72\\
ICC(2) & 0.58 & 0.76 & 0.85 & 0.67 & 0.73 & 0.96\\
\bottomrule
\multicolumn{7}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Lower triangle: Within-person correlations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
\end{tabular}}
\end{minipage}
\end{table}

>>>>

\caption{\label{tab:studentOutVarDescr}Student: Multilevel Core Variable Descriptives (Outgroup Contact Only)}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llcc}
\toprule
  & Core Need & Quality & Attitudes NL\\
\midrule
Core Need &  & 0.23 & 0.17\\
Quality & 0.23*** &  & 0.06\\
Attitudes NL & 0.16*** & 0.29*** & \\
\addlinespace
Grand Mean & 86.86 & 67.08 & 70.41\\
Between SD & 11.20 & 12.54 & 17.13\\
Within SD & 15.87 & 16.54 & 9.87\\
\addlinespace
ICC(1) & 0.14 & 0.24 & 0.72\\
ICC(2) & 0.58 & 0.73 & 0.96\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{4}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
\multicolumn{4}{l}{\rule{0pt}{1em}Lower triangle: Within-person correlations;}\\
\multicolumn{4}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
\end{tabular}}
\end{minipage}
\end{table}

### 2023-05-30 Tables/studentVarDescr.tex
descr tbl red

\caption{\label{tab:studentVarDescr}Student: Multilevel Core Variable Descriptives}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llccccc}
\toprule
  & Core Need & Competence & Autonomy & Relatedness & Quality & Attitudes NL\\
\midrule
Core Need &  & 0.61*** & 0.66*** & 0.42*** & 0.80*** & 0.10\\
Competence & 0.24*** &  & 0.74*** & 0.66*** & 0.75*** & 0.07\\
Autonomy & 0.15*** & 0.34*** &  & 0.58*** & 0.69*** & -0.04\\
Relatedness & 0.45*** & 0.29*** & 0.42*** &  & 0.55*** & -0.12\\
Quality & 0.17*** & 0.39*** & 0.08*** & 0.05** &  & 0.09\\
Attitudes NL & 0.35*** & 0.43*** & 0.11*** & 0.11*** & 0.13*** & \\
\addlinespace
Grand Mean & 84.87 & 72.55 & 82.59 & 61.21 & 83.77 & 67.26\\
Between SD & 9.17 & 14.47 & 11.21 & 13.36 & 9.12 & 18.64\\
Within SD & 20.33 & 21.17 & 16.06 & 28.74 & 16.80 & 9.40\\
ICC(1) & 0.15 & 0.30 & 0.32 & 0.17 & 0.20 & 0.80\\
ICC(2) & 0.89 & 0.95 & 0.95 & 0.90 & 0.88 & 0.99\\
\bottomrule
\multicolumn{7}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Lower triangle: Within-person correlations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
\end{tabular}}
\end{minipage}
\end{table}

>>>>

\caption{\label{tab:studentVarDescr}Student: Multilevel Core Variable Descriptives}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llcc}
\toprule
  & Core Need & Quality & Attitudes NL\\
\midrule
Core Need &  & 0.61*** & 0.03\\
Quality & 0.21*** &  & 0.02\\
Attitudes NL & 0.08*** & 0.09*** & \\
\addlinespace
Grand Mean & 84.87 & 74.51 & 67.26\\
Between SD & 9.17 & 11.24 & 18.64\\
Within SD & 20.33 & 16.59 & 9.40\\
\addlinespace
ICC(1) & 0.15 & 0.29 & 0.80\\
ICC(2) & 0.89 & 0.92 & 0.99\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{4}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
\multicolumn{4}{l}{\rule{0pt}{1em}Lower triangle: Within-person correlations;}\\
\multicolumn{4}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
\end{tabular}}
\end{minipage}
\end{table}

### 2023-05-30 Tables/workerOutVarDescr.tex
descr tbl red

\caption{\label{tab:workerOutVarDescr}Worker: Multilevel Core Variable Descriptives (Outgroup Contact Only)}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llccccc}
\toprule
  & Core Need & Competence & Autonomy & Relatedness & Quality & Attitudes NL\\
\midrule
Core Need &  & 0.83*** & 0.59*** & 0.26 & 0.36 & -0.02\\
Competence & 0.36*** &  & 0.88*** & 0.16 & 0.31 & -0.25\\
Autonomy & 0.29*** & 0.23*** &  & 0.21 & 0.35 & 0.03\\
Relatedness & 0.50*** & 0.38*** & 0.48*** &  & 0.25 & 0.18\\
Quality & 0.17** & 0.43*** & 0.27*** & 0.27*** &  & 0.23\\
Attitudes NL & 0.24*** & 0.37*** & 0.25*** & 0.37*** & 0.55*** & \\
\addlinespace
Grand Mean & 82.20 & 66.53 & 72.64 & 51.58 & 67.00 & 72.46\\
Between SD & 12.42 & 13.41 & 10.22 & 14.16 & 9.26 & 13.62\\
Within SD & 17.66 & 18.78 & 14.93 & 23.97 & 18.24 & 9.50\\
ICC(1) & 0.33 & 0.31 & 0.30 & 0.21 & 0.23 & 0.68\\
ICC(2) & 0.90 & 0.89 & 0.89 & 0.83 & 0.84 & 0.98\\
\bottomrule
\multicolumn{7}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Lower triangle: Within-person correlations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
\end{tabular}}
\end{minipage}
\end{table}

>>>>

\caption{\label{tab:workerOutVarDescr}Worker: Multilevel Core Variable Descriptives (Outgroup Contact Only)}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llcc}
\toprule
  & Core Need & Quality & Attitudes NL\\
\midrule
Core Need &  & 0.40 & -0.03\\
Quality & 0.37*** &  & 0.21\\
Attitudes NL & 0.27*** & 0.55*** & \\
\addlinespace
Grand Mean & 82.20 & 67.00 & 72.46\\
Between SD & 12.42 & 9.26 & 13.62\\
Within SD & 17.66 & 18.24 & 9.50\\
\addlinespace
ICC(1) & 0.33 & 0.23 & 0.68\\
ICC(2) & 0.90 & 0.84 & 0.98\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{4}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
\multicolumn{4}{l}{\rule{0pt}{1em}Lower triangle: Within-person correlations;}\\
\multicolumn{4}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
\end{tabular}}
\end{minipage}
\end{table}

### 2023-05-30 Tables/workerVarDescr.tex
descr tbl red

\caption{\label{tab:workerVarDescr}Worker: Multilevel Core Variable Descriptives}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llccccc}
\toprule
  & Core Need & Competence & Autonomy & Relatedness & Quality & Attitudes NL\\
\midrule
Core Need &  & 0.62*** & 0.49** & 0.00 & 0.33 & -0.20\\
Competence & 0.37*** &  & 0.69*** & -0.14 & 0.25 & -0.21\\
Autonomy & 0.32*** & 0.09** &  & -0.04 & 0.21 & 0.19\\
Relatedness & 0.45*** & 0.37*** & 0.35*** &  & 0.09 & -0.06\\
Quality & 0.05 & 0.42*** & 0.11*** & 0.12*** &  & 0.14\\
Attitudes NL & 0.10*** & 0.31*** & 0.15*** & 0.14*** & 0.44*** & \\
\addlinespace
Grand Mean & 77.95 & 62.10 & 72.17 & 55.29 & 67.00 & 71.49\\
Between SD & 14.68 & 13.72 & 12.09 & 14.59 & 9.26 & 12.91\\
Within SD & 20.83 & 20.89 & 15.15 & 23.29 & 17.43 & 8.11\\
ICC(1) & 0.29 & 0.28 & 0.38 & 0.28 & 0.23 & 0.70\\
ICC(2) & 0.96 & 0.95 & 0.97 & 0.95 & 0.83 & 0.99\\
\bottomrule
\multicolumn{7}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Lower triangle: Within-person correlations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
\end{tabular}}
\end{minipage}
\end{table}

>>>>

\caption{\label{tab:workerVarDescr}Worker: Multilevel Core Variable Descriptives}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llcc}
\toprule
  & Core Need & Quality & Attitudes NL\\
\midrule
Core Need &  & 0.46* & -0.18\\
Quality & 0.37*** &  & 0.19\\
Attitudes NL & 0.11*** & 0.50*** & \\
\addlinespace
Grand Mean & 77.95 & 67.00 & 71.49\\
Between SD & 14.68 & 9.26 & 12.91\\
Within SD & 20.83 & 17.43 & 8.11\\
\addlinespace
ICC(1) & 0.29 & 0.23 & 0.70\\
ICC(2) & 0.96 & 0.83 & 0.99\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{4}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
\multicolumn{4}{l}{\rule{0pt}{1em}Lower triangle: Within-person correlations;}\\
\multicolumn{4}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
\end{tabular}}
\end{minipage}
\end{table}
